### 2014-10-21 fundamentals/impl.tex
adds inheritance diagrams

\Cyclus, on the other hand, is primarily written in \texttt{C++} and relies on 
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms. 
Furthermore, the core infrastructure and related archetypes are free and 
open-source, BSD-3-clause licsened. No part of \Cyclus is proprietary or based 
on \gls{COTS}, Windows-based software. Accordingly, it can be easily deployed 
on large compute systems, such as high-throughput computing (HTC) systems.

Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. To date, it has been
used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
the \Cyclus library via its resource exchange API.

@@

Agent-based modeling is inherently object oriented.

@@

A key innovation in \Cyclus is implementing this generic API and modular 
architecture into a suite of dynamically loadable ``plugin'' libraries.  Though 
common in modern software architecture, such a ``plugin'' pattern has 
previously not been implemented in nuclear fuel cycle simulators in the 
literature.  In \Cyclus, this is made possible primarily by the clean, 
object-oriented \gls{API} and modern build system already described.

@@

Interchangability is accomplished by providing APIs that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. The \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{build} child agents and \textit{decommission} child
agents. The \Class{Trader} interface allows agent-agent interaction through the
trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
implement the \Class{Agent} interface and may optionally implement the
\Class{Trader} interface. For example, a \Class{Region} implements only the
\Class{Agent} interface, whereas a \Class{Facility} implements both the
\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
trade with another \Class{Facility}.

@@

The \Cyclus toolkit provides two useful modules for querying \Class{Material}
objects regarding physical parameters. First the \Class{MatQuery} module
provides a basic querying API, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, and also the amount of
aggregate nuclides, i.e., a \Class{Composition}, in a material. The
\Class{enrichment} module provides an API for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material given provided feed, product, and tails
assays.

>>>>

\Cyclus, on the other hand, is primarily written in \texttt{C++} and relies on 
libraries supported by Linux and UNIX (including Ubuntu and OSX) platforms. 
Furthermore, the core infrastructure and related archetypes are free and 
open-source, BSD-3-clause licsened. No part of \Cyclus is proprietary or based 
on \gls{COTS}, Windows-based software. Accordingly, it can be easily deployed 
on large compute systems, such as \acrlong{HTC} systems.

Cyclopts (\TODO{cite}), a proof of principle design and implementation of such a
system, uses UW-Madison's HTCondor HTC infrastructure to perform sensitivity
studies on \Cyclus' resource exchange optimization solvers. To date, it has been
used run over $10^4$ jobs, or (\TODO{compute time}) total compute hours, using
the \Cyclus library via its resource exchange \gls{API}.

@@

Agent-based modeling is inherently object oriented. Since agents are

@@

A key innovation in \Cyclus is implementing this generic API and modular 
architecture into a suite of dynamically loadable ``plugin'' libraries.  Though 
common in modern software architecture, such a ``plugin'' pattern has 
previously not been implemented in nuclear fuel cycle simulators in the 
literature.  In \Cyclus, this implementation maximizes the potential of the clean, 
object-oriented \gls{API} and modern build system already described.

@@

Interchangability is accomplished by providing APIs that define agent-to-agent
interaction and agent-to-environment interaction, primarily through the
\Class{Agent} and \Class{Trader} interfaces. Figure \ref{fig:agent_uml} shows 
the ``inheritance'' structure of the \Class{Agent} class in a \gls{UML} diagram 
format. It shows how the \Class{Agent} interface
provides a notion of parent-child hierarchichal relationship, where parents can
choose to \textit{build} child agents and \textit{decommission} child
agents. For the archetype developer, this interface provides enormous power, 
very simply. The \gls{API} exposes \Class{Agent} helpful functionality for 
interacting with the \Cyclus simulation kernel while abstracting away unnecessary 
detail.

\begin{figure}[htbp!]
\begin{center}
\includegraphics{agent_uml}
\end{center}
\caption{The inheritance structure in the \Class{Agent} class abstracts away 
unneccesary details while exposing powerful functionality.}
\label{fig:agent_uml}
\end{figure}

In a similar fasion, the \Class{Trader} interface allows agent-agent interaction through the
trading of \Class{Resource}s. Usabe archetypes in a \Cyclus simulation must
implement the \Class{Agent} interface and may optionally implement the
\Class{Trader} interface. For example, a \Class{Region} implements only the
\Class{Agent} interface, whereas a \Class{Facility} implements both the
\Class{Agent} and \Class{Trader} interface, allowing any \Class{Facility} to
trade with another \Class{Facility}.

@@

The \Cyclus toolkit provides two useful modules for querying \Class{Material}
objects regarding physical parameters. First the \Class{MatQuery} module
provides a basic querying \gls{API}, including the atom and mass fractions of
nuclides, the number of moles of a nuclide in a material, and also the amount of
aggregate nuclides, i.e., a \Class{Composition}, in a material. The
\Class{enrichment} module provides an \gls{API} for determining enrichment-related
parameters of a material, including the separative work units (SWU) and natural
uranium required to enrich a material given provided feed, product, and tails
assays.
